Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-20 analysis/paper/paper.Rmd
remove extra model vis that's not used

load(file = here("inst/extdata/m_e.Rda"))
load(file = here("inst/extdata/m_f.Rda"))
load(file = here("inst/extdata/m_g.Rda"))
load(file = here("inst/extdata/m_h.Rda"))
load(file = here("inst/extdata/m_i.Rda"))
load(file = here("inst/extdata/m_j.Rda"))
load(file = here("inst/extdata/m_k.Rda"))

pp_m_e <- pp_check(m_e)
pp_m_f <- pp_check(m_f)
pp_m_g <- pp_check(m_g)
pp_m_h <- pp_check(m_h)
pp_m_i <- pp_check(m_i)
pp_m_j <- pp_check(m_j)
pp_m_k <- pp_check(m_k)

# put them all together
p <- (pp_m_e | pp_m_f) / (pp_m_g | pp_m_h) / (pp_m_i | pp_m_j) / pp_m_k

>>>>

load(file = here("inst/extdata/m_e.Rda"))
load(file = here("inst/extdata/m_f.Rda"))
load(file = here("inst/extdata/m_g.Rda"))
load(file = here("inst/extdata/m_h.Rda"))
load(file = here("inst/extdata/m_i.Rda"))
load(file = here("inst/extdata/m_j.Rda"))

pp_m_e <- pp_check(m_e)
pp_m_f <- pp_check(m_f)
pp_m_g <- pp_check(m_g)
pp_m_h <- pp_check(m_h)
pp_m_i <- pp_check(m_i)
pp_m_j <- pp_check(m_j)

# put them all together
p <- (pp_m_e | pp_m_f) / (pp_m_g | pp_m_h) / (pp_m_i | pp_m_j)
